Cognate Priming: Report

### 2021-10-15 Rmd/report.Rmd
Render report
Disaggregate participant counts

# load packages
library(targets)
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(gt)
library(patchwork)
library(wesanderson)
library(shiny)
library(tidytext)
library(brms)
library(tidyverse)
library(here)

@@

### Stringent criteria {.tabset}

```{r child="report_00_participants_stringent.Rmd"}
```

### Relaxed criteria {.tabset}

@@

### Stringent criteria {.tabset}

```{r child="report_04_gca_stringent.Rmd"}
```

### Relaxed criteria {.tabset}

@@

### Stringent criteria {.tabset}

```{r child="report_05_attrition_stringent.Rmd"}
```

### Relaxed criteria {.tabset}

@@

### Stringent criteria {.tabset}

```{r child="report_06_vocabulary_stringent.Rmd"}
```

### Relaxed criteria {.tabset}

>>>>

# load packages
library(targets)
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(gt)
library(patchwork)
library(wesanderson)
library(shiny)
library(tidybayes)
library(brms)
library(tidytext)
library(brms)
library(tidyverse)
library(here)

@@

@@

@@

@@

### 2021-10-15 Rmd/report_00_participants_relaxed.Rmd
Disaggregate participant counts

```{r participants_summary_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

>>>>

```{r participants_summary_relaxed_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()
```

```{r participants_summary_relaxed_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp, test_language) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		test_language = md("**Language**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) 
	as_raw_html()
```

```{r participants_summary_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```
